# ex3 - Data Collection & Network Analysis

## Question 1

First, we load the requiered packeges:

```{r}
#install.packages("igraph")
#install.packages("digest")
#install.packages("rgl")
library("igraph")
library("digest")
library("rgl")
```

Then, we read the data into a graph

```{r}
ga.data <- read.csv('ga_edgelist.csv', header = T)
g <- graph.data.frame(ga.data,directed = F)
g$layout <- layout.fruchterman.reingold(g)
```

Next, we are asked about the biggest component in the graph, so we delete the vertices that are not part of it:
(we knew what the verticies were by plotting and inspecting the graph manually)

```{r}
g1 <- delete.vertices(g,c(24,11,10,12,25,26,31,13)) #delete anything but the biggest component
g1$layout <- layout.fruchterman.reingold(g1)
```

Now we will use the modified graph to check which actor has the highest cenerality rank by the 3 different methods:

### a)

using the following code:

```{r}
bet <- betweenness(g1, v = V(g1), directed = FALSE, weights = NULL,
            nobigint = TRUE, normalized = FALSE)
which(max(bet) == bet)
```
we discover that *sloan* is the actor with the highest bewtweenness rank.

### b)
